---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  fig.align = "center"
)
library(rjwsacruncher)
```

# rjwsacruncher

[![Travis Build Status](https://img.shields.io/travis/AQLT/rjwsacruncher.svg?logo=travis)](https://travis-ci.org/AQLT/rjwsacruncher)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/rjwsacruncher)](https://cran.r-project.org/package=rjwsacruncher)
[![CRAN last release](http://www.r-pkg.org/badges/last-release/rjwsacruncher)](https://cran.r-project.org/package=rjwsacruncher)
[![CRAN monthly downloads](http://cranlogs.r-pkg.org/badges/rjwsacruncher?color=lightgrey)](https://cran.r-project.org/package=rjwsacruncher)
[![CRAN downloads](http://cranlogs.r-pkg.org/badges/grand-total/rjwsacruncher?color=lightgrey)](https://cran.r-project.org/package=rjwsacruncher)


The goal of rjwsacruncher is to launch quickly and easily the [JWSACruncher](https://github.com/jdemetra/jwsacruncher) of [JDemetra+](https://github.com/jdemetra/jdemetra-app). The JWSACruncher is a console tool that allows to update a JDemetra+ workspace and to export the results without having to open JDemetra+. More details on the JWSACruncher can be found on <https://github.com/jdemetra/jwsacruncher/wiki>.

## Installation

```{r gh-installation, eval = FALSE}
# Install release version from CRAN
install.packages("rjwsacruncher")

# Install development version from GitHub
# install.packages("devtools")
devtools::install_github("AQLT/rjwsacruncher")
```

The JWSACruncher is not included in the package. It can be downloaded from GitHub (<https://github.com/jdemetra/jwsacruncher/releases>) or with the function `download_cruncher()`:

```{r, eval = FALSE}
library(rjwsacruncher)
# Directory where to save the JWSACruncher:
directory <- tempdir()
download_cruncher(directory)
```

Since the version 2.2.0, the JWSACruncher needs Java 8 or higher to run. If you cannot install it (for example for security reasons) you can install a portable version of 'Java' (that does not require administrator rights) and configure the JWSACruncher to use this portable version with the function `configure_jwsacruncher()`.

## Usage

The JWSACruncher can be easily runned with the function `cruncher_and_param()`. To use it, the path to the "Bin" folder of the JWSACruncher has to be defined. For example, if the JWSACruncher is under `D:/jdemetra-cli-2.2.2/`:
```{r, eval = FALSE}
options(cruncher_bin_directory = "D:/jdemetra-cli-2.2.2/bin/")
```
The export items can be changed with the function "default_matrix_item" and "default_tsmatrix_series":
```{r, eval = TRUE}
# To get the default values:
head(getOption("default_matrix_item"))
getOption("default_tsmatrix_series")
# To only export the seasonally adjusted series and its forecasts:
options(default_tsmatrix_series = c("sa", "sa_f"))
```
The run the JWSACruncher on the workspace `D:/workspace.xml` with the refresh policy "lastoutliers":
```{r, eval = FALSE}
cruncher_and_param(workspace = "D:/workspace.xml",
                   policy = "lastoutliers")
```
