---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  fig.align="center"
)
```

# rjwsacruncher

[![Travis Build Status](https://travis-ci.org/AQLT/rjwsacruncher.svg?branch=master)](https://travis-ci.org/AQLT/rjwsacruncher)
[![](https://img.shields.io/badge/lifecycle-experimental-orange.svg?logo=github)](https://www.tidyverse.org/lifecycle/#experimental)


The goal of rjwsacruncher is to launch quickly and easily the [JWSACruncher](https://github.com/jdemetra/jwsacruncher) of [JDemetra+](https://github.com/jdemetra/jdemetra-app). The JWSACruncher is a console tool that allows to update a JDemetra+ workspace's and to export the results without having to use JDemetra+. More details on the JWSACruncher can be found on <https://github.com/jdemetra/jwsacruncher/wiki>.

## Installation

The development version can be installed from GitHub:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("AQLT/rjwsacruncher", build_vignettes = TRUE)
```

The JWSACruncher is not included in the package. It can be downloaded from GitHub (<https://github.com/jdemetra/jwsacruncher/releases>) or with the function `download_cruncher()`;

```{r, eval = FALSE}
library(rjwsacruncher)
# Directory where to save the JWSACruncher:
directory <- tempdir()
download_cruncher(directory)
```


